The role of habitat quality in host metapopulations exposed to environmentally persistent pathogens. Or Identifying when environmentally persistent pathogens transform good habitat into ecological traps

### 2015-06-19 Manuscript/manuscript.tex
Updates to fig 2 to match fig 1
Updates to fig 3

\begin{figure}
%\includegraphics[scale=0.5]{figure/figure_2.pdf}
\centering
\caption{Differences between the median total effective population size of hosts on low quality patch distributions (quality between 0.23 to 1.24) and high quality patch distributions (quality between 0.76 and 1.77) as a function of disease-induced mortality ($\nu$) and the probability of direct transmission ($\delta$).  Reds indicate that high quality habitat distributions support higher median host population sizes than low quality habitat, primarily corresponding to pathogens with either very limited or very extensive spread. Conversely, blues indicate higher median host population sizes on low quality habitat distributions, corresponding to pathogens with intermediate levels of spread.  Panel columns show low (0.3, a), medium (1.0, b), and high (3.2, c) pathogen longevities.}
\label{highvlow}
\end{figure}

\begin{figure}
%\includegraphics[scale=0.5]{figure/figure_3.pdf}
\centering
\caption{Boxplots showing the range, over 100 replicate simulations, of susceptible (a), infectious (b), and total (c) host population sizes for high quality (red) and low quality (blue) habitat distributions.  Disease-induced mortality ($\nu$) and direct transmission rate ($\delta$) are fixed at values of 0.2 and 0.3, respectively.  Colored points show medians, while vertical lines indicate the outer-quartile ranges, with gray points indicating outliers (determined as points outside 1.5 times the inner-quartile range).  At low longevities, this pathogen is largely unable to persist and high quality habitat supports larger populations of susceptible hosts.  However, low qualiimplying that patch quality does not influence individual host fitness ty habitat is better able to maintain these susceptible hosts as the pathogen's longevity increases, leading to larger total population sizes.  PCC: took me a long time to understand this non-traditional boxplot. Personnally, I'd prefer a wide line for the inner quartiles and thin line for the outers. Then your eye is drawn towards and dwells on the most likely region rather than towards the unlikely region (the outer quartiles.)}
\label{popsizes}
\end{figure}

\begin{figure}
%\includegraphics[scale=0.4]{figure/figure_4.pdf}
\centering
\caption{Results from a single representative simulation with habitat quality uniformly distributed between 0.23 and 1.77, and a pathogen with a disease induced mortality of $\nu = 0.2$, a direct transmission rate of $\delta = 0.3$, and an envioronmental longevity equal to the expected residence time of a susceptible population on a unit quality patch (10 units of time here).  The top panel shows total proportion of patches occupied by susceptible (blue) and infectious (red) hosts over time.  The bottom panel shows the state -- susceptible (blue), infectious (red), or unoccupied (white) -- of individual patches through time.  Patches are stacked vertically with the lowest quality at the bottom and the highest quality at the top.  Note the overall more consistent occupancy on high quality habitat and the only very brief spurts of infectious occupancy on low quality habitat.}
\label{simvis}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.5]{figure/figure_2.pdf}
\centering
\caption{Differences between the median total effective population size of hosts on low quality patch distributions (quality between 0.23 to 1.24) and high quality patch distributions (quality between 0.76 and 1.77) as a function of disease-induced mortality ($\nu$) and the probability of direct transmission ($\delta$).  Reds indicate that high quality habitat distributions support higher median host population sizes than low quality habitat, primarily corresponding to pathogens with either very limited or very extensive spread. Conversely, blues indicate higher median host population sizes on low quality habitat distributions, corresponding to pathogens with intermediate levels of spread.  Panel columns show low (0.3, a), medium (1.0, b), and high (3.2, c) pathogen longevities.}
\label{highvlow}
\end{figure}

\begin{figure}
\includegraphics[scale=0.5]{figure/figure_3.pdf}
\centering
\caption{Boxplots showing the range, over 100 replicate simulations, of susceptible (a), infectious (b), and total (c) host population sizes for high quality (red) and low quality (blue) habitat distributions.  Disease-induced mortality ($\nu$) and direct transmission rate ($\delta$) are fixed at values of 0.2 and 0.3, respectively.  Colored points show medians, while vertical lines indicate the inner-quartile ranges, with horizontal lines indicating the minimum and maximum.  At low longevities, this pathogen is largely unable to persist and high quality habitat supports larger populations of susceptible hosts.  However, low quality habitat is better able to maintain these susceptible hosts as the pathogen's longevity increases, leading to larger total population sizes.}
\label{popsizes}
\end{figure}

\begin{figure}
\includegraphics[scale=0.4]{figure/figure_4.pdf}
\centering
\caption{Results from a single representative simulation with habitat quality uniformly distributed between 0.23 and 1.77, and a pathogen with a disease induced mortality of $\nu = 0.2$, a direct transmission rate of $\delta = 0.3$, and an envioronmental longevity equal to the expected residence time of a susceptible population on a unit quality patch (10 units of time here).  The top panel shows total proportion of patches occupied by susceptible (blue) and infectious (red) hosts over time.  The bottom panel shows the state -- susceptible (blue), infectious (red), or unoccupied (white) -- of individual patches through time.  Patches are stacked vertically with the lowest quality at the bottom and the highest quality at the top.  Note the overall more consistent occupancy on high quality habitat and the only very brief spurts of infectious occupancy on low quality habitat.}
\label{simvis}
\end{figure}
